---
title: "rodwell-ben-homework-01"
author: "Ben Rodwell"
date: "February 5, 2019"
output: html_document
---


---
title: "rodwell-bn-homework-01"
author: "Ben Rodwell"
date: "February 5, 2019"
output: html_document
---


# 1st Challenge

Create vector of the first line of gettysburg address 
```{r}
gettysburg <- "Four score and seven years ago our fathers brought forth on this continent a new nation, cinceived in Liberty, and dedicated to the proposition that all men are created equal."
```

Split into 1 word strings
```{r}
library(stringr)
gettysburgsplit <- str_split(gettysburg, " ", simplify = T)
gettysburgsplit
```

Extract every third element 
```{r}
gettysburgsplit[seq(from = 1, to = 30, by = 3)]
```

Create vector that is every third element of gettysburg address first line 
```{r}
gettysburgsplit3rd <- gettysburgsplit[seq(from = 1, to = 30, by = 3)]
gettysburgsplit3rd
```

Remove punctuation from same vector
```{r}
gettysburg3rdnopunctuation <- gsub("[[:punct:]]","",gettysburgsplit[seq(from = 1, to = 30, by = 3)])
gettysburg3rdnopunctuation
```



# 2nd Challenge

Extract columns 2, 3, and 6 from matrix
```{r}
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = F)
x <- m[,c(2,3,6)]
x
```

Extract rows 6 through 8 from matrix
```{r}
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = F)
x <- m[c(6:8),]
x
```

Extract rows 2 through 6 of columns 2 through 9 from matrix
```{r}
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = F)
x <- m[c(2:6),c(2:9)]
x
```



# 3rd Challenge

Construct 5x5x4x4 array with numbers in order from 400 to 100
```{r}
a <- array(400:1, dim = c(5,5,4,4))
```

Pull out the value in the first row and first column of the first layer of the fourth block
```{r}
a[1,1,1,2]
```

Pull out the the values in the second row and third column of the second layer of the each block
```{r}
a[2,3,2,]
```

Pull out the values in the firstst to fifth row, and the first to fifth column, from the third layer of the third block. In other words the entire third layer of the third block
```{r}
a[1:5,1:5,3,3]
```


# 4th Challenge

Make a list that captures a simplified primate taxonomy
```{r}
Lemuroidea <- list("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae", "Daubentoniidae")
Lorisoidea <- list("Lorisidae", "Galagidae")
Tarsioidea <- list("Tarsiidae")
Catarrhini <- list("Cercopithecidae", "Hylobatidae", "Hominidae")
Platyrrhini <- list("Cebidae", "Atelidae", "Pitheciidae")
Anthropoidea <- list(Platyrrhini,Catarrhini)
Strepsirhini <- list(Lemuroidea, Lorisoidea)
Haplorhini <- list(Anthropoidea, Tarsioidea)
Primates <- list(Haplorhini,Strepsirhini)
names(Lemuroidea) <- c("Strepsirhini")
names(Lorisoidea) <- c("Strepsirhini")
names(Strepsirhini) <- c("Primates")
names(Catarrhini)<- c("Anthropoidea")
names(Platyrrhini) <- c("Anthropoidea")
names(Tarsioidea) <- c("Anthropoidea")
Primates
```


# 5th Challenge

Create a matrix and coerce it into a data frame
```{r}
c5 <- matrix(data = c(3,0,1,23,1,2,33,1,1,42,0,1,41,0,2), nrow = 5, ncol = 3, byrow = TRUE)
c5 <- as.data.frame(c5)
```

Coerce the 2nd column into boolean logical values
```{r}
c5$V2 <- as.logical(c5$V2)                    
```

Coerce the 3rd column into factors
```{r}
c5$V3 <- as.factor(c5$V3)                    
```

Confirm that the changes have been made
```{r}
str(c5)
```

